Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-08 tex/paper1/paper1.tex
edits to the paper

\section{Observations}\label{sec:obs}

Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA
and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
waveband).  These wavebands were selected in order to obtain a wide
range of approximate temperatures in the solar corona.

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that the bright upper
transition region emission above active region plage (also known as
moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.

This suggests that a second model
$M_{2}$ for these regions should be considered.  The second model
$M_{2}$ has two contributions to the overall \Fps; a background
power-law of the form of $P_{1}$, and a contribution that is more
localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

The presence of a non-power law contribution to the \Fps\ does not
change the fact that the background emission is essentially power-law
like.  For the frequencies that have been of interest in coronal
seismology, the background power spectrum is therefore scale free on
average.  If there is no time-scale that can be used to remove a
background trend, then the time-series has to be analyzed without this
processing step.  A lack of awareness of the background red-noise
nature of the emission can cause problems in attempting to analyze for
the presence of narrow frequency band oscillations, as the following
example demonstrates.

@@

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{2010MNRAS.402..307V}.
Figure \ref{fig:comparison}(b) shows that the assumption of a
white-noise background and a 95\% confidence level leads to the
positive detection of significant oscillatory power in this time
series. Figure \ref{fig:comparison}(c) shows that the assumption of a
red-noise background with the same confidence level significantly
reduces the area for which a detection may be claimed.  This simulated
data, along with the results of Section \ref{sec:anal}, suggest that
when examining the wavelet transforms of time-series for wave packets,
a background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying red-noise as evidence for an oscillatory
signal.

Even this approach to identifying oscillatory power is not quite
complete, as it simply rejects the null hypothesis that the power
spectrum can be adequately explained by a red-noise power spectrum.
Model comparison similar to that described in Section \ref{sec:anal}
is required to prefer a model with oscillatory content over one
without. The difficulty in finding narrow-band features in Fourier
power spectra against a red-noise background power spectrum has been
recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model comparison and fitting
technique is directly applicable to the search for oscillatory power
in coronal time-series.

@@

The discussion of Section \ref{ssec:corseis} shows that red-noise
power spectra has a powerful effect on the claims of a detection of
narrow-frequency band oscillations in time-series.  When looking at
extended regions of coronal imaging data, evidence for the presence of
an oscillation in the corona is strengthened if it can be shown that
narrow frequency-band oscillations occur significantly above a
red-noise background signal in several neighboring pixels.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must somehow take into account the nature of the power
spectrum.  The power-law power spectrum itself lacks an easily
definable time-scale at or below which a background trend can be
defined.  Automated detection algorithns that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

As has been shown above, the assumption of a Gaussian-distributed
noise when red noise power-spectrum is actually present, coupled with
too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many detection algorithms do make
this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
approaches have yet to be tested assuming a red-noise background power
spectrum, and so their efficacy is unknown.
\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
wavelet-based approaches, and Figure \ref{fig:comparison} does suggest
that a red-noise background spectrum will make a significant
difference.

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on wave coherence, such
as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
red-noise background power spectrum: the discussion of Section
\ref{ssec:corseis} therefore suggests that the significance of any
claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background power law.

\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{2011soca.book.....A} describes
how a \PL\ \PS\ may obtained from such a distribution, and that
argument outlined below.

>>>>

\section{Observations}\label{sec:obs}
Data was obtained from SDO-AIA using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data at 12 second cadence was selected in the 171\AA
and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
waveband).  These wavebands were selected in order to obtain a wide
range of approximate temperatures in the solar corona.

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions.  Figures
\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
each model to the data.  Table \ref{tab:parameters} shows the fitted
parameter values and an error estimate for model $M_{2}$.  For details
on the fitting procedure, see Section \ref{sec:app:ind}.

@@

The presence of a non-power law contribution to the \Fps\ does not
change the fact that the background emission is essentially power-law
like.  For the frequencies that have been of interest in coronal
seismology, the background power spectrum is therefore scale free on
average.  If there is no time-scale that can be used to remove a
background trend, then the time-series has to be analyzed without this
processing step.  However, a lack of awareness of the background
red-noise nature of the emission can cause problems in attempting to
analyze for the presence of narrow frequency band oscillations, as the
following example demonstrates.

@@

Figure \ref{fig:comparison} shows how a red-noise power spectrum can
be mistakenly thought to contain an oscillatory signal.  The time
series (Figure \ref{fig:comparison}(a)) is constructed from a power
spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
following the construction procedure of \cite{2010MNRAS.402..307V}.
Figure \ref{fig:comparison}(b) shows that the assumption of a
white-noise background and a 95\% confidence level leads to the
positive detection of significant oscillatory power in this time
series. Figure \ref{fig:comparison}(c) shows that the assumption of a
red-noise background with the same confidence level significantly
reduces the area for which a detection may be claimed.  This simulated
data, along with the results of Section \ref{sec:anal}, suggest that
when examining the wavelet transforms of time-series for wave packets,
a background red-noise power spectrum should be assumed, along with
higher confidence levels, in order to minimize the effects of
mistakenly identifying random variations in the background power
spectrum as evidence for an oscillatory signal.

Even this approach to identifying oscillatory power is not quite
complete, as it simply rejects the null hypothesis that the power
spectrum can be adequately explained by a red-noise power spectrum.
Model comparison techniques similar to that described in Section
\ref{sec:anal} is required to prefer a model with oscillatory content
over one without. The difficulty in finding narrow-band features in
Fourier power spectra against a red-noise background power spectrum
has been recognized by \cite{2010MNRAS.402..307V} in the study of
XMM-Newton observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model fitting and comparison
technique is directly applicable to the search for oscillatory power
in coronal time-series.

@@

The discussion of Section \ref{ssec:corseis} shows that red-noise
power spectra has a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a {\it wave} in the corona is strengthened if it can be
shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is one key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must take into account the nature of the power spectrum.
The power-law power spectrum itself lacks an easily definable
time-scale at or below which a background trend can be defined.
Automated detection algorithms that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

As has been shown above, the assumption of a Gaussian-distributed
noise when a red noise power-spectrum is actually present, coupled
with too low a confidence level, can lead to misleading results when
looking for oscillatory signals.  Many wave detection algorithms do
make this assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
approaches have yet to be tested assuming a red-noise background power
spectrum, and so their efficacy is unknown.  However,
\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
wavelet-based approaches, and the discussion Section
\ref{ssec:corseis} does suggest that a red-noise background spectrum
will make a significant difference to the number of wave detections
found in the data.

All the automated detection algorithms described above attempt to find
individual pixels that are obviously oscillating at some frequency,
using the strength of the oscillation at that frequency (compared to
some assumption of the background) as the key quantity to measure.
These pixels are then clumped together and the quality of the signal
is then assessed.  Detection algorithms based on {\it wave coherence},
such as \cite{2008SoPh..252..321M}, implement wave detection through
finding spatially contiguous regions of the corona which are coherent
in a given frequency range.  The frequency range searched is based on
previous experience.  Oscillations that are detected propagating along
loops are often found by considering distance-time plots
\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
alternating brightening/darkening in those plots as a indicator of a
propagating wave.  This is essentially a coherence-based approach that
involves an implicit assessment of the likelihood that an oscillation
has been detected.  The basis of the assessment is a judgement that a
signal is seen in multiple contiguous pixels.  However, the results of
Section \ref{sec:anal} suggest that each pixel in these plots has a
red-noise background power spectrum: the discussion of Section
\ref{ssec:corseis} therefore suggests that the significance of any
claimed oscillation is much reduced.

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier power spectrum. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background power law.
\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
red-noise like power spectrum.  It is present in both wavebands
studied and in all the regions, and so parsimony suggests that the
mechanism of its creation is both similar and ubiquitous in all parts
of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
the sum of a distribution of a large number of energy deposition
events having different energies. \cite{2011soca.book.....A} describes
how a \PL\ \PS\ may obtained from such a distribution, and that
argument is outlined below.
